Clause size reduction with all-UIP Learning

### 2020-02-22 paper.tex
small change

\begin{document}
\maketitle              % typeset the header of the contribution
% 
\begin{abstract}
    Clause learning is an essential technique in \sat solvers.
    Almost all modern CDCL \sat solvers use the 1-UIP 
    clause learning scheme to learn new clauses from conflicts, 
    and our current understanding
    of \sat solving provides good reasons for using that scheme. In
    particular, the 1-UIP scheme yields asserting clauses, and these
    asserting clauses have minimum LBD among all possible asserting
    clauses. As a result of these advantages, other clause learning
    schemes, like $i$-UIP and all-UIP, that had been proposed in prior
    work are not used in modern solvers. In this paper, we propose a
    new technique for exploiting the all-UIP clause learning scheme. 
    Our technique $\allUip$ employs all-UIP learning under the
    constraint that the learnt clause's LBD does not increase (over the
    minimum established by the 1-UIP clause). $\allUip$ can generate
    clauses that are significantly smaller than the 1-UIP clause while
    preserving the minimum LBD. Unlike previous clause minimization
    methods, our technique is not limited to learning a sub-clause of
    the 1-UIP clause. It can instead learn a completely different
    clause. We show empirically that $\allUip$ can improve the
    performance of state of the art solvers.
\end{abstract}

>>>>

\begin{document}
\maketitle              % typeset the header of the contribution
% 
\begin{abstract}
    Clause learning is an essential technique in \sat solvers.
    Most of modern CDCL \sat solvers use the 1-UIP 
    clause learning scheme for learning new clauses from conflicts, 
    and our current understanding
    of \sat solving provides good reasons for using that scheme. In
    particular, the 1-UIP scheme yields asserting clauses, and these
    asserting clauses have minimum LBD among all possible asserting
    clauses. As a result of these advantages, other clause learning
    schemes, like $i$-UIP and all-UIP, that had been proposed in prior
    work are not used in modern solvers. In this paper, we propose a
    new technique for exploiting the all-UIP clause learning scheme. 
    Our technique $\allUip$ employs all-UIP learning under the
    constraint that the learnt clause's LBD does not increase (over the
    minimum established by the 1-UIP clause). $\allUip$ can learn
    clauses that are significantly smaller than the 1-UIP clause while
    preserving the minimum LBD. Unlike previous clause minimization
    methods, our technique is not limited to learning a sub-clause of
    the 1-UIP clause. It can instead learn a completely different
    clause with the same asserting literal. We show empirically 
    that $\allUip$ can improve the performance of state of the art solvers.
\end{abstract}
